\propertitle

### 2020-03-16 replies1_ncomp.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-03-16T16:48:19+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimfalse
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\firstdraft}{16 March 2020}
\newcommand*{\firstpublished}{16 March 2020}
\newcommand*{\updated}{\ifarxiv***\else\today\fi}
\newcommand*{\propertitle}{Sketch of replies to N. Comp. reviews%\\{\large ***}%
}% title uses LARGE; set Large for smaller
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{}
\newcommand*{\pdfauthor}{}
\newcommand*{\headauthor}{}
\newcommand*{\reporthead}{}%\ifarxiv\else Open Science Framework \href{https://doi.org/10.31219/osf.io/***}{\textsc{doi}:10.31219/osf.io/***}\fi}% Report number

@@

\textbullet\ If by \enquote{model} we mean only a family of probability
distribution, \eg\
\[\conds*{\exp\biggl[-\frac{(x-\mu)^{2}}{2\sigma^{2}}\biggr]\,\di x}{
    \mu\in\RR, \sigma \in\opop{0,\infty}}\;,\]
then model comparison is undefined, because we cannot calculate
$\p(D \| M_{i})$. Each distribution in the family assigns a different
probability, and it is not clear which should be chosen or how they should
be combined and why. A hypothesis is ill-defined, or at least useless, if
it does not allow us to assign a probability to the data. We need a
pre-data probability distribution for the model parameters, \eg\
$\pf(\mu,\sigma \| I)\,\di\mu\,\di\sigma$. \enquote{Model} must therefore
be redefined as a family of distributions \emph{and} a pre-data
distribution over such family. This redefinition has several consequences:

@@

Third, \emph{the evidence $\p(D \| M_{i}, I)$ of a model automatically
  takes care of its complexity}. This happens because the probability over
the data space is normalized. If $M_{1}$ has a typical data volume larger
than $M_{2}$, then it must also assign lower probability to each data point
in that volume, to ensure normalization. As a result, if the observed data
$D^{*}$ lie in the typical volumes of both models, then
$\pf(D^{*} \| M_{1},I)< \pf(D^{*} \| M_{2}, I)$: \emph{the evidence is
  automatically penalizing the larger model}. There is a continuous
trade-off between how typical the data is for each model and each model's
power. This is the so-called automatic Ockham razor of Bayes's theorem,
extensively explained by MacKay \citey{mackay1992}. And this is the reason
why we are personally satisfied with simply comparing the evidence for any
two models.

@@

\textbullet\

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-03-16T17:07:32+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimfalse
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\firstdraft}{16 March 2020}
\newcommand*{\firstpublished}{16 March 2020}
\newcommand*{\updated}{\ifarxiv***\else\today\fi}
\newcommand*{\propertitle}{Sketch of replies to N. Comp. reviews%\\{\large ***}%
}% title uses LARGE; set Large for smaller
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{}
\newcommand*{\pdfauthor}{}
\newcommand*{\headauthor}{}
\newcommand*{\reporthead}{}%\ifarxiv\else Open Science Framework \href{https://doi.org/10.31219/osf.io/***}{\textsc{doi}:10.31219/osf.io/***}\fi}% Report number

@@

\textbf{(A)} If by \enquote{model} we mean only a family of probability
distributions, \eg\ (apart from normalization)
\[\conds*{\exp\biggl[-\frac{(x-\mu)^{2}}{2\sigma^{2}}\biggr]\,\di x}{
    \mu\in\RR, \sigma \in\opop{0,\infty}}\;,\]
then model comparison is undefined, because we cannot calculate
$\p(D \| M_{i})$. Each distribution in the family assigns a different
probability, and it is not clear which should be chosen or how they should
be combined and why. A hypothesis is ill-defined, or at least useless, if
it does not allow us to assign a probability to the data. We need a
pre-data probability distribution for the model parameters, \eg\
$\pf(\mu,\sigma \| I)\,\di\mu\,\di\sigma$. \enquote{Model} must therefore
be redefined as a family of distributions \emph{and} a pre-data
distribution over such family. This redefinition has several consequences:

@@

Third, \emph{the evidence $\p(D \| M_{i}, I)$ of a model automatically
  takes care of its complexity}. This happens because the probability over
the data space is normalized. If $M_{1}$ has a typical-data volume larger
than $M_{2}$'s, then it must also assign lower probability to each data
point in that volume, to ensure normalization. As a result, if the observed
data $D^{*}$ lie in the typical volumes of both models, then
$\pf(D^{*} \| M_{1},I)< \pf(D^{*} \| M_{2}, I)$: \emph{the evidence is
  automatically penalizing the larger model}. There is a continuous
trade-off between how typical the data is for each model and each model's
power. This is the so-called automatic Ockham razor of Bayes's theorem,
extensively explained by MacKay
\citey{mackay1992}[also][\sect~28.1]{mackay1995_r2003}. And this is the
reason why we are personally satisfied with simply comparing the evidence
for any two models.

@@

\textbf{(B)} If by \enquote{model} we mean a specific distribution, \eg\
\[ \exp\biggl[-\frac{(x-5)^{2}}{18}\biggr]\,\di x \;,\] then two models can
of course be directly compared; that is $\p(D \|M_{i}, I)$ is well-defined.
In this case the \enquote{dimensionality} of the model is undefined,
however. The distribution above could be considered to belong to the family
$\set[\Big]{\exp\Bigl[-\frac{(x-\mu)^{2}}{18}\Bigr]}$, or
$\set[\Big]{\exp\Bigl[-\frac{(x-5)^{2}}{2\sigma^{2}}\Bigr]}$, or
$\set[\big]{\exp[f(x-5)]}$, and so on. A point in a manifold belongs to an
infinity of submanifolds.

Note that the property of having a minimal sufficient statistic is still
well-defined for a model in this sense, in an exchangeable context. The
model above has $\set{n, \widebar{x}, \widebar{x^{2}}}$ as minimal
sufficient statistics, where the bar denotes sample average. This does not
authorize us to see it as belonging to a sufficient-statistics family,
however.
